Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-10-30 thesis.Rmd
Ändrade två grammatik delar

Trauma is a major global public health concern. It causes over four million deaths, among those younger populations are the most affected[@noauthor_injuries_nodate]. Globally low and middle income countries are disproportionately affected, while high income countries like Sweden have lower overall number but the younger and economically active demographic are also affected. In Sweden between 2018 and 2021, the most common age demographic for trauma is the working aged population, between 18 and 64 years old[@noauthor_arsrapport_2022]. This not only leads to premature loss of life but also imposes a substantial socio-economic burden, due to long-term disabilities and rehabilitation needs[@noauthor_injuries_nodate].

@@

Trauma are generally divided into two groups, blunt and penetrating injury. The most common type in Sweden is blunt injury, constituting around 90% of all trauma. The most common causes for blunt trauma are traffic related and falls, which account for roughly ½ and ⅓ of all blunt trauma[@noauthor_arsrapport_2022].

>>>>

Trauma is a major global public health concern. It causes over four million deaths, among those younger populations are the most affected[@noauthor_injuries_nodate]. Globally low and middle income countries are disproportionately affected, while high income countries like Sweden have lower overall numbers but the younger and economically active demographic are also affected. In Sweden between 2018 and 2021, the most common age demographic for trauma is the working aged population, between 18 and 64 years old[@noauthor_arsrapport_2022]. This not only leads to premature loss of life but also imposes a substantial socio-economic burden, due to long-term disabilities and rehabilitation needs[@noauthor_injuries_nodate].

@@

Trauma is generally divided into two groups, blunt and penetrating injury. The most common type in Sweden is blunt injury, constituting around 90% of all trauma. The most common causes for blunt trauma are traffic related and falls, which account for roughly ½ and ⅓ of all blunt trauma[@noauthor_arsrapport_2022].
